{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-05 wacv_for_review.tex
Comments Replied
Another revision.

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems come with an image acquisition pipeline, and
a tremendous amount of progresses on computer vision research has been
made for the past few decades. However, to successfully deploy a
computer vision algorithm on any existing embedded systems, a vision
algorithm needs to satisfy, at least, two criteria with the assumption
of reasonably good performance: minimal, manual intervention after
deployment and small footprint of consuming computational
resources. While these criteria kept in mind, to develop a single,
target tracking system, we propose an ensemble of the kernelized
correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed, run-time performance, we deploy each of KCFs in turn. We
also developed a Bayes filter to minimize any potential drifts between
individual KCFs' transitions. Experimental results showed that the
performance of ours are, on average, 70.10\% for precision at 20
pixels, 53.00\% for success rate for OTB100 data, and 54.50\% and
40.2\% for UAV123 data. These results showed that our method is better
than existing ones over 5\% on precision on 20 pixels and 10-20\% on
AUC on average. Moreover our implementation ran at 340 fps for OTB100
and at 416 fps for UAV123 data that is faster than DCF (292 fps) for
OTB100 and KCF (292 fps), DCF (457 fps) for UAV123. To increase
flexibility of the proposed {\it E}nKCF running on various one-chip
computer, e.g., one with GPUs, we explored different levels of deep
features.
\end{abstract}

@@

In this paper, we propose a novel way of utilizing a multiple of the
KCFs \cite{henriques2015high} to effectively handle scale variations
and dynamic maneuvers of a target. To maintain or improve the run-time
performance of the original KCF (e.g., $\ge$ 300), we deploy three
KCFs in turn, instead of applying them on the same image frame
together. Each of these KCFs is designed to address specific
challenges, i.e., scale and translation. By alternating their
deployments, our algorithm will improve the performance of the
original KCF while preserving the efficient nature and small-footprint
of the KCF computation.

@@

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background, at least twice, bigger than that of the first filter,
$R_{t}^{S}$, \textit{target}+\textit{large background}. We set up {\it
  E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target as shown in Figure~\ref{fig:Filters}.

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

@@

The algorithm \ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF.
The order of running these three KCFs is important because each of
these filters aims at addressing different challenges; The
\textit{target+large background} translation filter, $R_{t}^{L}$, is
applied to the $i$th and $i+1$th image frames, another translation
filter, $R_{t}^{S}$ is applied to the $i+2$th and $i+3$th image
frames, and then the scale filter, $R_{s}$ is applied to the $i+4$the
image. This order repeats until the end of the image frames. The
translation filter, $R_{t}^{L}$, is intended to run right after the
scale filter, $R_s$, runs which is applied at every other $i+4$
frames. We run these filters in this way because we want to minimize
any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other two
frames before $R_{s}$ and right after two consecutive frames running
$R_{t}^{L}$. By repeating this order of learning KCFs, we can
integrate more discriminative shape features that cannot be learned by
$R_{t}^{L}$. This is because it incorporates a large area about
background in the learned model. The filter, $R_{t}^{L}$, uses shape
and color information together to recover from any potential drifts --
drifts could happen only looking the target's scale by the filter,
$R_{s}$.

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail each part of the KCF.

@@

We, first, use two hand-crafted features, fHoG \cite{felzenszwalb2010object} 
and color-naming \cite{li2014scale} in the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. 
This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
$30$ fps.

In particular, the translation filter, $R_{t}^{L}$, uses
both the fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} features to learn the large background area
around the target as shown in Figure~\ref{fig:Filters}.b. The color features 
compensate for the noisier fHoG features due to the large ROI considered 
by $R_{t}^{L}$. {\it Burak: You meant ``the
  color features are used to compensate for shape features' weakness
  -- what's weakness?}

  {\it YoungWoo : The weakness is the more background you include the noisier
  HoG features become.}
On the other hand, the color features is not assigned to the small area translation 
filter,  $R_{t}^{S}$, as it learns more useful fHoG features than $R_{t}^{L}$ due to smaller
padding size as seen in Figure~\ref{fig:Filters}.a. {\it Burak: color features are not used for $R_{t}^{S}$ because?
\it YoungWoo : We do not use color features because  $R_{t}^{S}$ concentrates on smaller ROI
than  $R_{t}^{L}$}. Finally, both fHoG and color-naming features are used for $R_{s}$, the scale filter, 
since the lower template resolution (64 x n)
assigned to $R_{s}$ leads to less discriminative shape
features as in Figure~\ref{fig:Filters}.c. Smaller template size is assigned to $R_{s}$ as it estimates
the scale by correlating the filter with multiple ROIs as shown in
alg.~\ref{alg:MKCF}.  This way, we can keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By doing so, we can avoid
fluctuating run-time performance among KCFs which is not desired in embedded
systems.

\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance. {\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}
  {\it YoungWoo : EnkCF with deep features improved the performance on the same set of data.}
This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
devised to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.

@@

\textbf{Particle Filter for Smoothing Transition among KCFs} As
explained earlier, the {\it E}nKCF updates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential drifts, we
developed a Bayes filter that incorporates a target's motion to smooth
any intermediate outputs from individual KCFs of the {\it E}nKCF. In
particular, we use a particle filter to estimate the target's image
coordinate based on the {\it E}nKCF's outputs. A particle filter is a
sequential Monte Carlo method that uses a finite number of particles
or samples to estimate the posterior probability density of a state of
the system \cite{thrun2005probabilistic}. In this study, the state
represents a target's pixel coordinates and its motion. In particular,
the state of the particle filter, $X_t$, is represented by $\lbrace x,
y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates
of the target's centroid, $v_x$ and $v_y$ are the estimated velocity
along the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. And then the particle filter uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
\sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)$, where $w_{p}$
denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
size of the window as that of a confidence map. Alternatively one can
also use the Euclidean distance of particles to the location of
maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
{\it Burak: We cannot just begin with a detail. You need to give the
  readers an overview of what they'll be reading.}

In this section, we evaluate the performance of the proposed {\it E}nKCF
tracker and its variants on the object tracking benchmarks. 
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.
We first evaluate the performance of {\it E}nKCF 
with hand-crafted features.  With this tracker, we aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
To further improve the performance, we employed deeper features to the scale filter as it learns smaller ROI
than the translation filters.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems come with an image acquisition pipeline, and
a tremendous amount of progresses on computer vision research has been
made for the past few decades. However, to successfully deploy a
computer vision algorithm on any existing embedded systems, a vision
algorithm needs to satisfy, at least, two criteria with the assumption
of reasonably good performance: minimal, manual intervention after
deployment and small footprint of consuming computational
resources. While these criteria kept in mind, to develop a single,
target tracking system, we propose an ensemble of the kernelized
correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed, run-time performance, we deploy each of KCFs in turn. We
also developed a Bayes filter to minimize any potential drifts between
individual KCFs' transitions. Experimental results showed that the
performance of ours are, on average, 70.10\% for precision at 20
pixels, 53.00\% for success rate for OTB100 data, and 54.50\% and
40.2\% for UAV123 data. These results showed that our method is better
than existing ones over 5\% on precision on 20 pixels and 10-20\% on
AUC on average. Moreover our implementation ran at 340 fps for OTB100
and at 416 fps for UAV123 data that is faster than DCF (292 fps) for
OTB100 and KCF (292 fps), DCF (457 fps) for UAV123. In addition, to
increase flexibility of the proposed {\it E}nKCF running on various
one-chip computer, e.g., one with GPUs, we explored different levels
of deep features.
\end{abstract}

@@

In this paper, we propose a novel way of utilizing a multiple of the
KCFs \cite{henriques2015high} to effectively handle scale variations
and dynamic maneuvers of a target. To maintain or even improve the
run-time performance of the original KCF (e.g., $\ge$ 300), we deploy
three KCFs in turn, instead of applying them on the same image frame
together. Each of these KCFs is designed to address specific
challenges, i.e., scale and translation. By alternating their
deployments, our algorithm will improve the performance of the
original KCF while preserving the efficient nature and small-footprint
of the KCF computation.

@@

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background, at least twice, bigger than that of the first filter,
$R_{t}^{S}$, \textit{target}+\textit{large background}. We set up {\it
  E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target. {\it Burak: We only explained two kinds of
  filters: translation and scale filter. But we do have two filters
  for target's translation, $R_{t}^{S}$ and $R_{t}^{L}$. Revise the
  the sentence about translation filter with details.}

{\it Burak: DO NOT use ``Figure~\ref{fig:Filters}'' just write ``Figure \ref{fig:Filters}''}
\begin{comment}
 as shown in Figure~\ref{fig:Filters}.
\end{comment}

Figure \ref{fig:Filters} shows examples of three filters.

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features: the
  translation filter, \textit{target+small background}, another
  translation filter for capturing the bigger background,
  \textit{target+large background}, and the scale filter,
  \textit{target-only} depicted in their Hanning windows and expected
  Gaussian response.}
\label{fig:Filters}
\end{figure}

@@

The algorithm \ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF.
The order of running these three KCFs is important because each of
these filters aims at addressing different challenges; The
\textit{target+large background} translation filter, $R_{t}^{L}$, is
applied to the $i$th and $i+1$th image frames, another translation
filter, $R_{t}^{S}$ is applied to the $i+2$th and $i+3$th image
frames, and then the scale filter, $R_{s}$ is applied to the $i+4$the
image. This order repeats until the end of the image frames. The
translation filter, $R_{t}^{L}$, is intended to run right after the
scale filter, $R_s$, runs which is applied at every other $i+4$
frames. We run these filters in this way because we want to minimize
any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other two
frames before $R_{s}$ and right after two consecutive frames running
$R_{t}^{L}$. By repeating this order of learning KCFs, we can
integrate more discriminative shape features that cannot be learned by
learning only $R_{t}^{L}$. This is because it incorporates a large
area about background in the learned model. The filter, $R_{t}^{L}$,
uses shape and color information together to recover from any
potential drifts -- drifts potentially occurring only by learning the
target's scale with the scale filter, $R_{s}$.

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that may learn noisy
shape features due to its large search area. In what follows, we will
detail each part of the {\it E}nKCF.

@@

{\it Burak: This section does NOT connect to the previous section.}

We, first, use two hand-crafted features, fHoG
\cite{felzenszwalb2010object} and color-naming \cite{li2014scale} in
the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. {\it Burak:
  Figure \ref{fig:Filters} is placed a way before this sentence -- We
  don't want the readers to look back while reading a certain
  sentence. And I don't see fHoG and color-naming or descriptions of
  them from that Figure.}

This version of the {\it E}nKCF is designed to execute a single,
target tracking on any embedded systems at $30$ fps.

The translation filter, $R_{t}^{L}$, uses both the fHoG
\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
features to learn the large background area around the target. Figure
\ref{fig:Filters} (b) shows an example of this translation filter. The
color features are also used to make the feature vector more
discriminative. In other words, for the case that the fHoG is the only
feature, the bigger the area for HoG is the more noises the resulting
fHoG feature contains. Adding color information to the feature vector
will make the feature vector more robust to the noises from the
background around the target. However, this is not the case for the
translation filter, $R_{t}^{S}$, for capturing a smaller area. This is
because the translation filter, {\it target + small background}, does
not contain much of the background area around the target. Figure
\ref{fig:Filters} (a) shows an example of this translation filter.

\begin{comment}
On the other hand, the color features is not assigned to the small
area translation filter, $R_{t}^{S}$, as it learns more useful fHoG
features than $R_{t}^{L}$ due to smaller padding size as seen in
Figure~\ref{fig:Filters}.a. {\it Burak: color features are not used
  for $R_{t}^{S}$ because?  \it YoungWoo : We do not use color
  features because $R_{t}^{S}$ concentrates on smaller ROI than
  $R_{t}^{L}$}.
\end{comment}

We use both fHoG and color-naming features for the scale filter, $R_{s}$.

{\it Burak: The following sentence was NOT clear. Rewrite. Look at
  what I wrote about the translation filter, $R_{t}^{L}$.}  since the
lower template resolution (64 x n) assigned to $R_{s}$ leads to less
discriminative shape features as in Figure~\ref{fig:Filters}.c.

Smaller template size is assigned to $R_{s}$ as it estimates the scale
by correlating the filter with multiple ROIs as shown in
alg.~\ref{alg:MKCF}.  {\it Burak: Try to minimize such a
  BACK-reference. No one like looking back the parts of a paper you
  already read!}

This way, we can keep the run-time complexity of the $R_{S}$ similar
to $R_{t}^{L}$ and $R_{t}^{S}$ that only run correlation filter on a
single ROI. {\it Burak: Why do we need to keep the run-time complexity
  of $R_{S}$ and $R_{t}^{L}$ the same?}

By doing so, we can avoid fluctuating run-time performance among KCFs
which is not desired in embedded systems. {\it Burak: By doing what,
  you can avoid fluctuating run-time performance? Rewrite this
  sentence in connection with the above-mentioned!}

\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance.

{\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}

{\it YoungWoo :
  EnkCF with deep features improved the performance on the same set of
  data.}

{\it Burak: If EnKCF w/ deep features improved the performance of
  EnKCF on the same set of data, why didn't you plot their curves
  together? And if this is true, we'll have to revise the abstract and
  introduction as well!}

This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
devised to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.

@@

\textbf{Particle Filter for Smoothing Transition among KCFs}

{\it Burak: Does what this section explains still hold good? If what
  this section explains still makes sense, the translation filter,
  $R_{t}^{L}$ doesn't do a good job. Isn't it? If it's not, revise
  this section.}

As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential drifts, we
developed a Bayes filter that incorporates a target's motion to smooth
any intermediate outputs from individual KCFs of the {\it E}nKCF. In
particular, we use a particle filter to estimate the target's image
coordinate based on the {\it E}nKCF's outputs. A particle filter is a
sequential Monte Carlo method that uses a finite number of particles
or samples to estimate the posterior probability density of a state of
the system \cite{thrun2005probabilistic}. In this study, the state
represents a target's pixel coordinates and its motion. In particular,
the state of the particle filter, $X_t$, is represented by $\lbrace x,
y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates
of the target's centroid, $v_x$ and $v_y$ are the estimated velocity
along the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. And then the particle filter uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
\sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)$, where $w_{p}$
denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
size of the window as that of a confidence map. Alternatively one can
also use the Euclidean distance of particles to the location of
maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
In this section, we evaluate the performance of the proposed {\it E}nKCF
tracker and its variants on the object tracking benchmarks. 
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.
We first evaluate the performance of {\it E}nKCF 
with hand-crafted features.  With this tracker, we aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

{\it Burak: What happened to the experiment of DNN features? You'll
  have to preview whatever the readers will read below this section!}

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects
with deep feature encodings to boost tracking performance by about
$5\%$ on embedded systems with GPUs.  To further improve the
performance, we employed deeper features to the scale filter as it
learns smaller ROI than the translation filters. {\it Burak: We
  employed deeper features and then what happened?}
